---
title: "Network Meta-Analysis of Interventions for Scabies"
author: "Dr Amiel Nazer C. Bermudez"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
subtitle: "Itch resolution, 3-6 weeks"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
```

```{r, echo = FALSE, include = FALSE}
# Load dataset 
ires36_pairs <- read.csv("~/ires36_pairs.csv")     # Contrast format

# Rename variables
names(ires36_pairs)[names(ires36_pairs) == "X_design"] <- "design"
names(ires36_pairs)[names(ires36_pairs) == "X_t1"] <- "t1"
names(ires36_pairs)[names(ires36_pairs) == "X_t2"] <- "t2"
names(ires36_pairs)[names(ires36_pairs) == "X_y"] <- "y"
names(ires36_pairs)[names(ires36_pairs) == "X_stderr"] <- "stderr"
names(ires36_pairs)[names(ires36_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs$ycorr <- (-1)*(ires36_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_pairs <- merge(t1labels, ires36_pairs, by = "t1")
ires36_pairs <- merge(t2labels, ires36_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs <- merge(studychar, ires36_pairs, by = "study")

# Obtain overall sample size
ires36_long <- read.csv("~/ires36_v1.csv")
sum(ires36_long$n)
```


# **Network meta-analysis proper**

## *Network meta-analysis*
```{r, echo = FALSE}
ires36.nmeta <- netmeta(TE = ycorr,
                        seTE = stderr,
                        treat1 = t1_lab,
                        treat2 = t2_lab,
                        studlab = study,
                        data = ires36_pairs,
                        sm = "RR",
                        fixed = FALSE,
                        random = TRUE,
                        reference.group = "Permethrin",
                        details.chkmultiarm = TRUE,
                        sep.trts = " vs ")
ires36.nmeta
```

### Sample size for main analysis
```{r, echo = FALSE}
sum(ires36_long$n)
```

## *Contribution matrix*
```{r, echo = FALSE}
nc <- netcontrib(ires36.nmeta)
nc
```

## *All pairwise comparisons*
```{r, echo = FALSE}
pair.ires36 <- netpairwise(ires36.nmeta, random = TRUE)
forest(pair.ires36)
```

## *Total inconsistency based on the full design-by-treatment interaction random-effects model*
```{r, echo = FALSE}
decomp.design(ires36.nmeta)
```

### Q based on a FE model to assess consistency in the whole network, within designs, and between designs
```{r, echo = FALSE}
decomp.design(ires36.nmeta)$Q.decomp
```

### Design-specific decomposition of the within-designs Q of the FE model
```{r, echo = FALSE}
decomp.design(ires36.nmeta)$Q.het.design
```

### Between-designs Q based on RE model with tau.within estimated embedded in a full design-by-treatment interaction
```{r, echo = FALSE}
decomp.design(ires36.nmeta)$Q.inc.random
```

## *Network graph*
```{r, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# Create vector of node size based on sample size
ptsize <- 30*c(0.08, 0.03, 0.31, 0.19, 0.35, 0.03)

# Edge thickness based on number of studies
netgraph(ires36.nmeta, 
         multiarm = FALSE,
         plastic = FALSE,
         thickness = "number.of.studies",
         number.of.studies = FALSE,
         col = "#424549",
         points = TRUE,
         cex.points = ptsize,
         col.points = "#ffa500")

netgraph(ires36.nmeta, 
         multiarm = FALSE,
         plastic = FALSE,
         thickness = "number.of.studies",
         number.of.studies = TRUE,
         col = "#424549",
         points = TRUE,
         cex.points = ptsize,
         col.points = "#ffa500")
```

## *Direct and indirect evidence visualization*
```{r, echo = FALSE}
direct.evidence.plot(ires36.nmeta, random = TRUE)
```

## *League table*
```{r, echo = FALSE}
# Generate effect table
netleague <- netleague(ires36.nmeta, bracket = "(", digits = 2)
netleague

# Save results
# write.csv(netleague$random, "~/netleague.csv")
```

## *Treatment rankings*
```{r, echo = FALSE}
# Based on p-score
netrank(ires36.nmeta, small.values = "bad",
        method = "P-score", random = TRUE)
  
# Based on SUCRA
set.seed(12345)
netrank(ires36.nmeta, small.values = "bad",
        method = "SUCRA", nsim = 10000, random = TRUE)

# Rankogram
set.seed(12345)
rank <- rankogram(ires36.nmeta, small.values = "bad",
                  nsim = 10000, random = TRUE, digits = 6)
rank
plot(rank)
plot(rank, cumulative.rankprob = TRUE)
```

### *Obtain mean ranks by simulation*
```{r, echo = FALSE}
set.seed(12345)

results <- list()

for(i in 1:10000)
  {
  sim_result <- netrank(ires36.nmeta, small.values = "bad", 
                        method = "SUCRA", random = TRUE)
  results[[i]] <- sim_result$ranking.random
}

df <- as.data.frame(results)
new.names <- paste0("sim", 1:10000)
names(df) <- new.names

ranks <- apply(df, 2, function(x) rank(-x, ties.method = "first"))
means <- rowMeans(ranks)
means
```

## *Forest plot*
```{r, echo = FALSE}
fplot <- forest(ires36.nmeta, 
         reference.group = "Permethrin",
         sortvar = TE,
         smlab = paste("Itch resolution, 3-6 weeks \n",
                       "Main analysis"),
         drop.reference.group = FALSE,
         label.left = "Favors permethrin",
         label.right = "Favors treatment")
```


# **Evaluating the validity of results**

## *Network heat plot, fixed-effects*
```{r, echo = FALSE}
netheat(ires36.nmeta, random = FALSE)
```

## *Network heat plot, random-effects*
```{r, echo = FALSE}
netheat(ires36.nmeta, random = TRUE)
```

## *Net splitting to check for loop-specific inconsistency*
```{r, echo = FALSE}
netsplit(ires36.nmeta, random = TRUE)
netsplit(ires36.nmeta) %>% 
  forest()
```

## *Comparison-adjusted funnel plot*
```{r, echo = FALSE, warning = FALSE}
funnel(ires36.nmeta, 
       order = c("Benzyl benzoate", "Crotamiton", "Lindane", 
                 "Oral IVM", "Permethrin", "Topical IVM"),
       pooled = "random",
       pch = c(1:8),
       col = c("blue", "red", "purple", "forestgreen", "grey", 
               "green", "black", "brown"),
       legend = TRUE,
       linreg = TRUE)
```


# **Subgroup analysis**

## *By risk of bias / study quality*

### Risk of bias: Low to some concerns (code: sg_robbin = 0)
```{r, echo = FALSE}
ires36.nmeta.rob0 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_robbin==0))
ires36.nmeta.rob0
```

### Risk of bias: High (code: sg_robbin = 1)
```{r, echo = FALSE}
ires36.nmeta.rob1 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_robbin==1))
ires36.nmeta.rob1
```

### Combined forest plot
```{r, echo = FALSE}
fp.rob <- netbind(ires36.nmeta.rob0, ires36.nmeta.rob1,
                  name = c("Low / some concerns ROB", "High ROB"),
                  col.study = c("red", "black"),
                  col.square = c("red", "black"))

forest(fp.rob,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By risk of bias"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.rob <- rma(yi = y, sei = stderr, mods = as.factor(sg_robbin), data = ires36_pairs, 
               method = "REML", test = "knha")
reg.rob
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_robbin == 0]))
with(ires36_long, sum(n[sg_robbin == 1]))
```

## *By age groups*

### Age group: Children (code: sg_agegrp = 1)
```{r, echo = FALSE}
ires36.nmeta.age1 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_agegrp==1))
ires36.nmeta.age1
```

### Age group: Adults (code: sg_agegrp = 2)
Cannot fit model due to non-conformable array

### Age group: Children + Adults (code: sg_agegrp = 3)
```{r, echo = FALSE}
ires36.nmeta.age3 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_agegrp==3))
ires36.nmeta.age3
```

### Combined forest plot
```{r, echo = FALSE}
fp.age <- netbind(ires36.nmeta.age1, ires36.nmeta.age3,
                  name = c("Children", "Children + Adults"),
                  col.study = c("red", "blue"),
                  col.square = c("red", "blue"))

forest(fp.age,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By age group"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.age <- rma(yi = y, sei = stderr, mods = as.factor(sg_agegrp), data = ires36_pairs, 
               method = "REML", test = "knha")
reg.age
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_agegrp == 1]))
with(ires36_long, sum(n[sg_agegrp == 2]))
with(ires36_long, sum(n[sg_agegrp == 3]))
```

## *By country income*

### Country income: High income (code: sg_countryinc = 1)
```{r, echo = FALSE}
ires36.nmeta.inc1 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_countryinc==1))
ires36.nmeta.inc1
```

### Country income: Low to middle income (code: sg_countryinc = 2)
```{r, echo = FALSE}
ires36.nmeta.inc2 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires36_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_countryinc==2))
ires36.nmeta.inc2
```

### Combined forest plot
```{r, echo = FALSE}
fp.inc <- netbind(ires36.nmeta.inc1, ires36.nmeta.inc2,
                  name = c("High income", "Low to middle income"),
                  col.study = c("red", "black"),
                  col.square = c("red", "black"))

forest(fp.inc,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By country income group"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.inc <- rma(yi = y, sei = stderr, mods = as.factor(sg_countryinc), data = ires36_pairs, 
               method = "REML", test = "knha")
reg.inc
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_countryinc == 1]))
with(ires36_long, sum(n[sg_countryinc == 2]))
```

## *By confirmed versus non-confirmed parasitological diagnosis*

### Parasitological diagnosis not confirmed (code: sg_paradx = 0)
```{r, echo = FALSE}
ires36.nmeta.paradx0 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires36_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_paradx==0))
ires36.nmeta.paradx0
```

### Parasitological diagnosis confirmed (code: sg_paradx = 1)
Cannot fit model due to absence of data on comparator

### Combined forest plot
Not applicable

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.paradx <- rma(yi = y, sei = stderr, mods = as.factor(sg_paradx), data = ires36_pairs, 
               method = "REML", test = "knha")
reg.paradx
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_paradx == 0]))
with(ires36_long, sum(n[sg_paradx == 1]))
```

## *By treatment of scabies prior to trial entry*

### Without prior treatment of scabies (code: sg_prevtx = 0)
```{r, echo = FALSE}
ires36.nmeta.prevtx0 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires36_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_prevtx==0))
ires36.nmeta.prevtx0
```

### With prior treatment of scabies (code: sg_prevtx = 1)
Cannot fit model due to the presence of two separate sub-networks

### Combined forest plot
Not applicable

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.prevtx <- rma(yi = y, sei = stderr, mods = as.factor(sg_prevtx), data = ires36_pairs, 
                  method = "REML", test = "knha")
reg.prevtx
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_prevtx == 0]))
with(ires36_long, sum(n[sg_prevtx == 1]))
```

## *By presence of cointerventions*

### Without cointerventions (code: sg_cointerv = 0)
```{r, echo = FALSE}
ires36.nmeta.cointerv0 <- netmeta(TE = ycorr,
                                  seTE = stderr,
                                  treat1 = t1_lab,
                                  treat2 = t2_lab,
                                  studlab = study,
                                  data = ires36_pairs,
                                  sm = "RR",
                                  fixed = FALSE,
                                  random = TRUE,
                                  reference.group = "Permethrin",
                                  details.chkmultiarm = TRUE,
                                  sep.trts = " vs ",
                                  subset = (sg_cointerv==0))
ires36.nmeta.cointerv0
```

### With cointerventions (code: sg_cointerv = 1)
Cannot fit model due to non-conformable arrays

### Not stated (code: sg_cointerv = 2)
```{r, echo = FALSE}
ires36.nmeta.cointerv2 <- netmeta(TE = ycorr,
                                  seTE = stderr,
                                  treat1 = t1_lab,
                                  treat2 = t2_lab,
                                  studlab = study,
                                  data = ires36_pairs,
                                  sm = "RR",
                                  fixed = FALSE,
                                  random = TRUE,
                                  reference.group = "Permethrin",
                                  details.chkmultiarm = TRUE,
                                  sep.trts = " vs ",
                                  subset = (sg_cointerv==2))
ires36.nmeta.cointerv2
```

### Combined forest plot
```{r, echo = FALSE}
fp.cointerv <- netbind(ires36.nmeta.cointerv0, ires36.nmeta.cointerv2,
                       name = c("Without co-interventions", "Not stated"),
                       col.study = c("red", "blue"),
                       col.square = c("red", "blue"))

forest(fp.cointerv,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By co-interventions"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.cointerv <- rma(yi = y, sei = stderr, mods = as.factor(sg_cointerv), data = ires36_pairs, 
                  method = "REML", test = "knha")
reg.cointerv
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_cointerv == 0]))
with(ires36_long, sum(n[sg_cointerv == 1]))
with(ires36_long, sum(n[sg_cointerv == 2]))
```

## *By % skin involvement*

### Severity, < 50% involvement (code: sg_severebase = 0)
```{r, echo = FALSE}
ires36.nmeta.severebase0 <- netmeta(TE = ycorr,
                                    seTE = stderr,
                                    treat1 = t1_lab,
                                    treat2 = t2_lab,
                                    studlab = study,
                                    data = ires36_pairs,
                                    sm = "RR",
                                    fixed = FALSE,
                                    random = TRUE,
                                    reference.group = "Permethrin",
                                    details.chkmultiarm = TRUE,
                                    sep.trts = " vs ",
                                    subset = (sg_severebase==0))
ires36.nmeta.severebase0
```

### Severity, >/= 50% involvement (code: sg_severebase = 1)
Cannot fit model due to the presence of two separate sub-networks

### Severity, unspecified (code: sg_severebase = 2)
```{r, echo = FALSE}
ires36.nmeta.severebase2 <- netmeta(TE = ycorr,
                                    seTE = stderr,
                                    treat1 = t1_lab,
                                    treat2 = t2_lab,
                                    studlab = study,
                                    data = ires36_pairs,
                                    sm = "RR",
                                    fixed = FALSE,
                                    random = TRUE,
                                    reference.group = "Permethrin",
                                    details.chkmultiarm = TRUE,
                                    sep.trts = " vs ",
                                    subset = (sg_severebase==2))
ires36.nmeta.severebase2
```

### Combined forest plot
```{r, echo = FALSE}
fp.severebase <- netbind(ires36.nmeta.severebase0, ires36.nmeta.severebase2,
                         name = c("< 50%", "Unspecified"),
                         col.study = c("red", "blue"),
                         col.square = c("red", "blue"))

forest(fp.severebase,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By % skin involment"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.severebase <- rma(yi = y, sei = stderr, mods = as.factor(sg_severebase), data = ires36_pairs, 
                      method = "REML", test = "knha")
reg.severebase
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_severebase == 0]))
with(ires36_long, sum(n[sg_severebase == 1]))
with(ires36_long, sum(n[sg_severebase == 2]))
```

## *By industry funding*

### Non-industry funded (code: sg_funding = 0)
```{r, echo = FALSE, warning = FALSE}
ires36.nmeta.funding0 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires36_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==0))
ires36.nmeta.funding0
```

### Industry funded (code: sg_funding = 1)
```{r, echo = FALSE, warning = FALSE}
ires36.nmeta.funding1 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires36_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==1))
ires36.nmeta.funding1
```

### Funding not specified (code: sg_funding = 2)
```{r, echo = FALSE, warning = FALSE}
ires36.nmeta.funding2 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires36_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==2))
ires36.nmeta.funding2
```

### Combined forest plot
```{r, echo = FALSE}
fp.funding <- netbind(ires36.nmeta.funding0, ires36.nmeta.funding1, ires36.nmeta.funding2,
                         name = c("Non-industry funded", "Industry funded", "Funding not specified"),
                         col.study = c("red", "black","blue"),
                         col.square = c("red", "black","blue"))

forest(fp.funding,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By industry funding"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.funding <- rma(yi = y, sei = stderr, mods = as.factor(sg_funding), data = ires36_pairs, 
                   method = "REML", test = "knha")
reg.funding
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires36_long, sum(n[sg_funding == 0]))
with(ires36_long, sum(n[sg_funding == 1]))
with(ires36_long, sum(n[sg_funding == 2]))
```


# *Data management for sensitivity analyses*

## *Best case scenario*
```{r, echo = FALSE}
# Load dataset 
ires36_bcs <- read.csv("~/ires36_bcs.csv") 

# Rename variables
names(ires36_bcs)[names(ires36_bcs) == "X_design"] <- "design"
names(ires36_bcs)[names(ires36_bcs) == "X_t1"] <- "t1"
names(ires36_bcs)[names(ires36_bcs) == "X_t2"] <- "t2"
names(ires36_bcs)[names(ires36_bcs) == "X_y"] <- "y"
names(ires36_bcs)[names(ires36_bcs) == "X_stderr"] <- "stderr"
names(ires36_bcs)[names(ires36_bcs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_bcs$ycorr <- (-1)*(ires36_bcs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_bcs <- merge(t1labels, ires36_bcs, by = "t1")
ires36_bcs <- merge(t2labels, ires36_bcs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_bcs <- merge(studychar, ires36_bcs, by = "study")

# Obtain overall sample size
ires_long <- read.csv("~/ires36_v1.csv")
sum(ires_long$bcs_n)
```

## *Worst case scenario*
```{r, echo = FALSE}
# Load dataset 
ires36_wcs <- read.csv("~/ires36_wcs.csv") 

# Rename variables
names(ires36_wcs)[names(ires36_wcs) == "X_design"] <- "design"
names(ires36_wcs)[names(ires36_wcs) == "X_t1"] <- "t1"
names(ires36_wcs)[names(ires36_wcs) == "X_t2"] <- "t2"
names(ires36_wcs)[names(ires36_wcs) == "X_y"] <- "y"
names(ires36_wcs)[names(ires36_wcs) == "X_stderr"] <- "stderr"
names(ires36_wcs)[names(ires36_wcs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_wcs$ycorr <- (-1)*(ires36_wcs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_wcs <- merge(t1labels, ires36_wcs, by = "t1")
ires36_wcs <- merge(t2labels, ires36_wcs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_wcs <- merge(studychar, ires36_wcs, by = "study")

# Obtain overall sample size
ires_long <- read.csv("~/ires36_v1.csv")
sum(ires_long$wcs_n)
```

## *Excludes Taplin 1990*
```{r, echo = FALSE}
# Load dataset 
ires36_pairs <- read.csv("~/ires36_pairs.csv")     # Contrast format

# Rename variables
names(ires36_pairs)[names(ires36_pairs) == "X_design"] <- "design"
names(ires36_pairs)[names(ires36_pairs) == "X_t1"] <- "t1"
names(ires36_pairs)[names(ires36_pairs) == "X_t2"] <- "t2"
names(ires36_pairs)[names(ires36_pairs) == "X_y"] <- "y"
names(ires36_pairs)[names(ires36_pairs) == "X_stderr"] <- "stderr"
names(ires36_pairs)[names(ires36_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs$ycorr <- (-1)*(ires36_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_pairs <- merge(t1labels, ires36_pairs, by = "t1")
ires36_pairs <- merge(t2labels, ires36_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs <- merge(studychar, ires36_pairs, by = "study")

# Subset to exclude Taplin 1990
ires36_pairs_con1 <- filter(ires36_pairs, study!="Taplin1990")

# Obtain overall sample size
ires36_long <- read.csv("~/ires36_v1.csv")
ires36_long_con1 <- filter(ires36_long, study!="Taplin1990")
sum(ires36_long_con1$n)
```

## *Includes studies with preferred itch definition*
```{r, echo = FALSE}
# Load dataset 
ires36_pairs <- read.csv("~/ires36_pairs.csv")     # Contrast format

# Rename variables
names(ires36_pairs)[names(ires36_pairs) == "X_design"] <- "design"
names(ires36_pairs)[names(ires36_pairs) == "X_t1"] <- "t1"
names(ires36_pairs)[names(ires36_pairs) == "X_t2"] <- "t2"
names(ires36_pairs)[names(ires36_pairs) == "X_y"] <- "y"
names(ires36_pairs)[names(ires36_pairs) == "X_stderr"] <- "stderr"
names(ires36_pairs)[names(ires36_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs$ycorr <- (-1)*(ires36_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_pairs <- merge(t1labels, ires36_pairs, by = "t1")
ires36_pairs <- merge(t2labels, ires36_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs <- merge(studychar, ires36_pairs, by = "study")

# Subset to studies with preferred definition of itch
ires36_pairs_itchdef <- filter(ires36_pairs, sensi_itchdef==0)

# Obtain overall sample size
ires36_long <- read.csv("~/ires36_v1.csv")
ires36_long_itchdef <- filter(ires36_long, sensi_itchdef==0)
sum(ires36_long_itchdef$n)
```

## *Includes studies with preferred outcome definition*
```{r, echo = FALSE}
# Load dataset 
ires36_pairs <- read.csv("~/ires36_pairs.csv")     # Contrast format

# Rename variables
names(ires36_pairs)[names(ires36_pairs) == "X_design"] <- "design"
names(ires36_pairs)[names(ires36_pairs) == "X_t1"] <- "t1"
names(ires36_pairs)[names(ires36_pairs) == "X_t2"] <- "t2"
names(ires36_pairs)[names(ires36_pairs) == "X_y"] <- "y"
names(ires36_pairs)[names(ires36_pairs) == "X_stderr"] <- "stderr"
names(ires36_pairs)[names(ires36_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs$ycorr <- (-1)*(ires36_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_pairs <- merge(t1labels, ires36_pairs, by = "t1")
ires36_pairs <- merge(t2labels, ires36_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs <- merge(studychar, ires36_pairs, by = "study")

# Subset to studies with preferred outcome definition
ires36_pairs_outcomedef <- filter(ires36_pairs, sensi_outcomedef==1)

# Obtain overall sample size
ires36_long <- read.csv("~/ires36_v1.csv")
ires36_long_outcomedef <- filter(ires36_long, sensi_outcomedef==1)
sum(ires36_long_outcomedef$n)
```

## *Includes studies with low / some concerns risk of bias*
```{r, echo = FALSE}
# Load dataset 
ires36_pairs <- read.csv("~/ires36_pairs.csv")     # Contrast format

# Rename variables
names(ires36_pairs)[names(ires36_pairs) == "X_design"] <- "design"
names(ires36_pairs)[names(ires36_pairs) == "X_t1"] <- "t1"
names(ires36_pairs)[names(ires36_pairs) == "X_t2"] <- "t2"
names(ires36_pairs)[names(ires36_pairs) == "X_y"] <- "y"
names(ires36_pairs)[names(ires36_pairs) == "X_stderr"] <- "stderr"
names(ires36_pairs)[names(ires36_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs$ycorr <- (-1)*(ires36_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires36_pairs <- merge(t1labels, ires36_pairs, by = "t1")
ires36_pairs <- merge(t2labels, ires36_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs <- merge(studychar, ires36_pairs, by = "study")

# Subset to low/some concerns ROB
ires36_pairs_rob <- filter(ires36_pairs, sg_robbin==0)

# Obtain overall sample size
ires36_long <- read.csv("~/ires36_v1.csv")
ires36_long_rob <- filter(ires36_long, sg_robbin==0)
sum(ires36_long_rob$n)
```

## *OIVM and PERM split dose*
```{r, echo = FALSE}
# Load dataset 
ires36_pairs_splitdose <- read.csv("~/ires36_splitdose.csv") 

# Rename variables
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_design"] <- "design"
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_t1"] <- "t1"
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_t2"] <- "t2"
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_y"] <- "y"
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_stderr"] <- "stderr"
names(ires36_pairs_splitdose)[names(ires36_pairs_splitdose) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires36_pairs_splitdose$ycorr <- (-1)*(ires36_pairs_splitdose$y)

# Combine with treatment labels
t1labels_splitdose <- read.csv("~/t1labels_splitdose.csv")
t2labels_splitdose <- read.csv("~/t2labels_splitdose.csv")
ires36_pairs_splitdose <- merge(t1labels_splitdose, ires36_pairs_splitdose, by = "t1")
ires36_pairs_splitdose <- merge(t2labels_splitdose, ires36_pairs_splitdose, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires36_v1.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires36_pairs_splitdose <- merge(studychar, ires36_pairs_splitdose, by = "study")
```
