---
title: "Network Meta-Analysis of Interventions for Scabies"
author: "Dr Amiel Nazer C. Bermudez"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
subtitle: "Itch resolution, 1-2 weeks"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
library(rgl)
```

```{r, echo = FALSE, include = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Import dataset in long format
ires12_long <- read.csv("~/ires12_v3.csv")
```


# **Network meta-analysis proper**

## *Network meta-analysis*
```{r, echo = FALSE}
ires12.nmeta <- netmeta(TE = ycorr,
                        seTE = stderr,
                        treat1 = t1_lab,
                        treat2 = t2_lab,
                        studlab = study,
                        data = ires12_pairs,
                        sm = "RR",
                        fixed = FALSE,
                        random = TRUE,
                        reference.group = "Permethrin",
                        details.chkmultiarm = TRUE,
                        sep.trts = " vs ")
ires12.nmeta
```

### Sample size for main analysis
```{r, echo = FALSE}
sum(ires12_long$n)
```

## *Contribution matrix*
```{r, echo = FALSE}
nc <- netcontrib(ires12.nmeta)
nc
```

## *All pairwise comparisons*
```{r, echo = FALSE}
pair.ires12 <- netpairwise(ires12.nmeta, random = TRUE)
pair.ires12
forest(pair.ires12)
```

## *Total inconsistency based on the full design-by-treatment interaction random-effects model*
```{r, echo = FALSE}
decomp.design(ires12.nmeta)
```

### Q based on a FE model to assess consistency in the whole network, within designs, and between designs
```{r, echo = FALSE}
decomp.design(ires12.nmeta)$Q.decomp
```

### Design-specific decomposition of the within-designs Q of the FE model
```{r, echo = FALSE}
decomp.design(ires12.nmeta)$Q.het.design
```

### Between-designs Q based on RE model with tau.within estimated embedded in a full design-by-treatment interaction
```{r, echo = FALSE}
decomp.design(ires12.nmeta)$Q.inc.random
```

## *Network graph*
```{r, echo = FALSE, warning = FALSE, error = FALSE, message = FALSE}
# Create vector of node size based on sample size
ptsize <- 30*c(0.10, 0.03, 0.08, 0.34, 0.30, 0.01, 0.07, 0.08)

# Edge thickness based on number of studies
netgraph(ires12.nmeta, 
         multiarm = FALSE,
         plastic = FALSE,
         thickness = "number.of.studies",
         number.of.studies = FALSE,
         col = "#424549",
         points = TRUE,
         cex.points = ptsize,
         col.points = "#ffa500")

netgraph(ires12.nmeta, 
         multiarm = FALSE,
         plastic = FALSE,
         thickness = "number.of.studies",
         number.of.studies = TRUE,
         col = "#424549",
         points = TRUE,
         cex.points = ptsize,
         col.points = "#ffa500")
```

## *Direct and indirect evidence visualization*
```{r, echo = FALSE}
direct.evidence.plot(ires12.nmeta, random = TRUE)
```

## *League table*
```{r, echo = FALSE}
# Generate effect table
netleague <- netleague(ires12.nmeta, bracket = "(",  digits = 2)
netleague

# Save results
# write.csv(netleague$random, "~/netleague_ires12.csv")
```

## *Treatment rankings*
```{r, echo = FALSE}
# Based on p-score
netrank(ires12.nmeta, small.values = "bad",
        method = "P-score", random = TRUE)
  
# Based on SUCRA
set.seed(12345)
netrank(ires12.nmeta, small.values = "bad",
        method = "SUCRA", nsim = 10000, random = TRUE)

# Rankogram
set.seed(12345)
rank <- rankogram(ires12.nmeta, small.values = "bad",
                  nsim = 10000, random = TRUE, digits = 6)
rank
plot(rank)
plot(rank, cumulative.rankprob = TRUE)
```

### *Obtain mean ranks by simulation*
```{r, echo = FALSE}
set.seed(12345)

results <- list()

for(i in 1:10000)
  {
  sim_result <- netrank(ires12.nmeta, small.values = "bad", 
                        method = "SUCRA", random = TRUE) 
  results[[i]] <- sim_result$ranking.random
}

df <- as.data.frame(results)
new.names <- paste0("sim", 1:10000)
names(df) <- new.names

ranks <- apply(df, 2, function(x) rank(-x, ties.method = "first"))
means <- rowMeans(ranks)
means
```

## *Forest plot*
```{r, echo = FALSE}
fplot <- forest(ires12.nmeta, 
         reference.group = "Permethrin",
         sortvar = TE,
         smlab = paste("Itch resolution, 1-2 weeks \n",
                       "Main analysis"),
         drop.reference.group = FALSE,
         label.left = "Favors permethrin",
         label.right = "Favors treatment")
```


# **Evaluating the validity of results**

## *Network heat plot, fixed-effects*
```{r, echo = FALSE}
netheat(ires12.nmeta, random = FALSE)
```

## *Network heat plot, random-effects*
```{r, echo = FALSE}
netheat(ires12.nmeta, random = TRUE)
```

## *Net splitting to check for loop-specific inconsistency*
```{r, echo = FALSE}
netsplit(ires12.nmeta, random = TRUE)
netsplit(ires12.nmeta) %>% 
  forest()
```

## *Comparison-adjusted funnel plot*
```{r, echo = FALSE, warning = FALSE}
funnel(ires12.nmeta, 
       order = c("Benzyl benzoate", "Crotamiton", "Lindane", "Oral IVM",
                 "Permethrin", "Pyrethrin", "Sulfur", "Topical IVM"),
       pooled = "random",
       pch = c(1:13),
       col = c("blue", "red", "purple", "forestgreen", "grey", 
               "green", "black", "brown", "orange", "pink", 
               "khaki", "plum", "aquamarine"),
       legend = TRUE,
       linreg = TRUE)
```


# **Subgroup analysis**

## *By risk of bias / study quality*

### Risk of bias: Low to some concerns (code: sg_robbin = 0)
```{r, echo = FALSE}
ires12.nmeta.rob0 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires12_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_robbin==0))
ires12.nmeta.rob0
```

### Risk of bias: High (code: sg_robbin = 1)
```{r, echo = FALSE}
ires12.nmeta.rob1 <- netmeta(TE = ycorr,
                             seTE = stderr,
                             treat1 = t1_lab,
                             treat2 = t2_lab,
                             studlab = study,
                             data = ires12_pairs,
                             sm = "RR",
                             fixed = FALSE,
                             random = TRUE,
                             reference.group = "Permethrin",
                             details.chkmultiarm = TRUE,
                             sep.trts = " vs ",
                             subset = (sg_robbin==1))
ires12.nmeta.rob1
```

### Combined forest plot
```{r, echo = FALSE}
fp.bias <- netbind(ires12.nmeta.rob0, ires12.nmeta.rob1,
                   name = c("Low/some concerns ROB", "High ROB"),
                   col.study = c("red", "black"),
                   col.square = c("red", "black"))

forest(fp.bias,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By risk of bias"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.rob <- rma(yi = y, sei = stderr, mods = as.factor(sg_robbin), data = ires12_pairs, 
               method = "REML", test = "knha")
reg.rob
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_robbin == 0]))
with(ires12_long, sum(n[sg_robbin == 1]))
```

## *By age groups*
Not performed

## *By country income*
Not performed

## *By primary versus recurrent scabies*
Not performed

## *By confirmed versus non-confirmed parasitological diagnosis*

### Parasitological diagnosis not confirmed (code: sg_paradx = 0)
```{r, echo = FALSE}
ires12.nmeta.paradx0 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires12_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_paradx==0))
ires12.nmeta.paradx0
```

### Parasitological diagnosis confirmed (code: sg_paradx = 1)
```{r, echo = FALSE}
ires12.nmeta.paradx1 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires12_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_paradx==1))
ires12.nmeta.paradx1
```

### Combined forest plot
```{r, echo = FALSE}
fp.paradx <- netbind(ires12.nmeta.paradx0, ires12.nmeta.paradx1,
                     name = c("Without parasitological confirmation", "With parasitological confirmation"),
                     col.study = c("red", "black"),
                     col.square = c("red", "black"))

forest(fp.paradx,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By parasitological confirmation"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.paradx <- rma(yi = y, sei = stderr, mods = as.factor(sg_paradx), data = ires12_pairs, 
               method = "REML", test = "knha")
reg.paradx
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_paradx == 0]))
with(ires12_long, sum(n[sg_paradx == 1]))
```

## *By treatment of scabies prior to trial entry*

### Without prior treatment of scabies (code: sg_prevtx = 0)
```{r, echo = FALSE}
ires12.nmeta.prevtx0 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires12_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_prevtx==0))
ires12.nmeta.prevtx0
```

### With prior treatment of scabies (code: sg_prevtx = 1)
```{r, echo = FALSE}
ires12.nmeta.prevtx1 <- netmeta(TE = ycorr,
                                seTE = stderr,
                                treat1 = t1_lab,
                                treat2 = t2_lab,
                                studlab = study,
                                data = ires12_pairs,
                                sm = "RR",
                                fixed = FALSE,
                                random = TRUE,
                                reference.group = "Permethrin",
                                details.chkmultiarm = TRUE,
                                sep.trts = " vs ",
                                subset = (sg_prevtx==1))
ires12.nmeta.prevtx1
```

### Combined forest plot
```{r, echo = FALSE}
fp.prevtx <- netbind(ires12.nmeta.prevtx0, ires12.nmeta.prevtx1,
                     name = c("Without scabies treatment prior to entry", 
                              "With scabies treatment prior to entry"),
                     col.study = c("red", "black"),
                     col.square = c("red", "black"))

forest(fp.prevtx,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By scabies tx prior to entry"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.prevtx <- rma(yi = y, sei = stderr, mods = as.factor(sg_prevtx), data = ires12_pairs, 
                  method = "REML", test = "knha")
reg.prevtx
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_prevtx == 0]))
with(ires12_long, sum(n[sg_prevtx == 1]))
```

## *By simultaneous treatment of close contacts*
Not performed

## *By % skin involvement*

### Severity, < 50% involvement (code: sg_severebase = 0)
```{r, echo = FALSE}
ires12.nmeta.severebase0 <- netmeta(TE = ycorr,
                                    seTE = stderr,
                                    treat1 = t1_lab,
                                    treat2 = t2_lab,
                                    studlab = study,
                                    data = ires12_pairs,
                                    sm = "RR",
                                    fixed = FALSE,
                                    random = TRUE,
                                    reference.group = "Permethrin",
                                    details.chkmultiarm = TRUE,
                                    sep.trts = " vs ",
                                    subset = (sg_severebase==0))
ires12.nmeta.severebase0
```

### Severity, >/= 50% involvement (code: sg_severebase = 1)
```{r, echo = FALSE}
ires12.nmeta.severebase1 <- netmeta(TE = ycorr,
                                    seTE = stderr,
                                    treat1 = t1_lab,
                                    treat2 = t2_lab,
                                    studlab = study,
                                    data = ires12_pairs,
                                    sm = "RR",
                                    fixed = FALSE,
                                    random = TRUE,
                                    reference.group = "Permethrin",
                                    details.chkmultiarm = TRUE,
                                    sep.trts = " vs ",
                                    subset = (sg_severebase==1))
ires12.nmeta.severebase1
```

### Severity, unspecified (code: sg_severebase = 2)
```{r, echo = FALSE}
ires12.nmeta.severebase2 <- netmeta(TE = ycorr,
                                    seTE = stderr,
                                    treat1 = t1_lab,
                                    treat2 = t2_lab,
                                    studlab = study,
                                    data = ires12_pairs,
                                    sm = "RR",
                                    fixed = FALSE,
                                    random = TRUE,
                                    reference.group = "Permethrin",
                                    details.chkmultiarm = TRUE,
                                    sep.trts = " vs ",
                                    subset = (sg_severebase==2))
ires12.nmeta.severebase2
```

### Combined forest plot
```{r, echo = FALSE}
fp.severebase <- netbind(ires12.nmeta.severebase0, ires12.nmeta.severebase1, ires12.nmeta.severebase2,
                     name = c("< 50%", "> 50%", "Unspecified"),
                     col.study = c("red", "black", "blue"),
                     col.square = c("red", "black", "blue"))

forest(fp.severebase,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By % skin involvement"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.severebase <- rma(yi = y, sei = stderr, mods = as.factor(sg_severebase), data = ires12_pairs, 
                      method = "REML", test = "knha")
reg.severebase
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_severebase == 0]))
with(ires12_long, sum(n[sg_severebase == 1]))
with(ires12_long, sum(n[sg_severebase == 2]))
```

## *By presence of co-interventions*

### Without co-interventions (code: sg_cointerv = 0)
```{r, echo = FALSE}
ires12.nmeta.cointerv0 <- netmeta(TE = ycorr,
                               seTE = stderr,
                               treat1 = t1_lab,
                               treat2 = t2_lab,
                               studlab = study,
                               data = ires12_pairs,
                               sm = "RR",
                               fixed = FALSE,
                               random = TRUE,
                               reference.group = "Permethrin",
                               details.chkmultiarm = TRUE,
                               sep.trts = " vs ",
                               subset = (sg_cointerv==0))
ires12.nmeta.cointerv0
```

### With co-interventions (code: sg_cointerv = 1)
```{r, echo = FALSE}
ires12.nmeta.cointerv1 <- netmeta(TE = ycorr,
                               seTE = stderr,
                               treat1 = t1_lab,
                               treat2 = t2_lab,
                               studlab = study,
                               data = ires12_pairs,
                               sm = "RR",
                               fixed = FALSE,
                               random = TRUE,
                               reference.group = "Permethrin",
                               details.chkmultiarm = TRUE,
                               sep.trts = " vs ",
                               subset = (sg_cointerv==1))
ires12.nmeta.cointerv1
```

### Co-interventions not specified (code: sg_cointerv = 2)
```{r, echo = FALSE}
ires12.nmeta.cointerv2 <- netmeta(TE = ycorr,
                               seTE = stderr,
                               treat1 = t1_lab,
                               treat2 = t2_lab,
                               studlab = study,
                               data = ires12_pairs,
                               sm = "RR",
                               fixed = FALSE,
                               random = TRUE,
                               reference.group = "Permethrin",
                               details.chkmultiarm = TRUE,
                               sep.trts = " vs ",
                               subset = (sg_cointerv==2))
ires12.nmeta.cointerv2
```

### Combined forest plot
```{r, echo = FALSE}
fp.cointerv <- netbind(ires12.nmeta.cointerv0, ires12.nmeta.cointerv1, ires12.nmeta.cointerv2,
                     name = c("Without co-interventions", "With co-interventions", "Unspecified"),
                     col.study = c("red", "black", "blue"),
                     col.square = c("red", "black", "blue"))

forest(fp.cointerv,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By co-interventions"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.cointerv <- rma(yi = y, sei = stderr, mods = as.factor(sg_cointerv), data = ires12_pairs, 
                    method = "REML", test = "knha")
reg.cointerv
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_cointerv == 0]))
with(ires12_long, sum(n[sg_cointerv == 1]))
with(ires12_long, sum(n[sg_cointerv == 2]))
```

## *By industry funding*

### Non-industry funded (code: sg_funding = 0)
```{r, echo = FALSE, warning = FALSE}
ires12.nmeta.funding0 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires12_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==0))
ires12.nmeta.funding0
```

### Industry funded (code: sg_funding = 1)
```{r, echo = FALSE, warning = FALSE}
ires12.nmeta.funding1 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires12_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==1))
ires12.nmeta.funding1
```

### Funding not specified (code: sg_funding = 2)
```{r, echo = FALSE, warning = FALSE}
ires12.nmeta.funding2 <- netmeta(TE = ycorr,
                                 seTE = stderr,
                                 treat1 = t1_lab,
                                 treat2 = t2_lab,
                                 studlab = study,
                                 data = ires12_pairs,
                                 sm = "RR",
                                 fixed = FALSE,
                                 random = TRUE,
                                 reference.group = "Permethrin",
                                 details.chkmultiarm = TRUE,
                                 sep.trts = " vs ",
                                 subset = (sg_funding==2))
ires12.nmeta.funding2
```

### Combined forest plot
```{r, echo = FALSE}
fp.funding <- netbind(ires12.nmeta.funding0, ires12.nmeta.funding1, ires12.nmeta.funding2,
                      name = c("Non-industry funded", "Industry funded", "Unspecified"),
                      col.study = c("red", "black", "blue"),
                      col.square = c("red", "black", "blue"))

forest(fp.funding,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By industry funding"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.funding <- rma(yi = y, sei = stderr, mods = as.factor(sg_funding), data = ires12_pairs, 
                   method = "REML", test = "knha")
reg.funding
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_funding == 0]))
with(ires12_long, sum(n[sg_funding == 1]))
with(ires12_long, sum(n[sg_funding == 2]))
```

## *By timing of outcome*

### 1 week (code: sg_outcometime = 1)
```{r, echo = FALSE}
ires12.nmeta.outcometime1 <- netmeta(TE = ycorr,
                                     seTE = stderr,
                                     treat1 = t1_lab,
                                     treat2 = t2_lab,
                                     studlab = study,
                                     data = ires12_pairs,
                                     sm = "RR",
                                     fixed = FALSE,
                                     random = TRUE,
                                     reference.group = "Permethrin",
                                     details.chkmultiarm = TRUE,
                                     sep.trts = " vs ",
                                     subset = (sg_outcometime==1))
ires12.nmeta.outcometime1
```

### 2 weeks (code: sg_outcometime = 2)
```{r, echo = FALSE}
ires12.nmeta.outcometime2 <- netmeta(TE = ycorr,
                                     seTE = stderr,
                                     treat1 = t1_lab,
                                     treat2 = t2_lab,
                                     studlab = study,
                                     data = ires12_pairs,
                                     sm = "RR",
                                     fixed = FALSE,
                                     random = TRUE,
                                     reference.group = "Permethrin",
                                     details.chkmultiarm = TRUE,
                                     sep.trts = " vs ",
                                     subset = (sg_outcometime==2))
ires12.nmeta.outcometime2
```

### Combined forest plot
```{r, echo = FALSE}
fp.outcometime <- netbind(ires12.nmeta.outcometime1, ires12.nmeta.outcometime2,
                          name = c("1 week", "2 weeks"),
                          col.study = c("red", "black"),
                          col.square = c("red", "black"))

forest(fp.outcometime,
       col.by = "black", addrow.subgroups = TRUE,
       fontsize = 10, spacing = 0.7, squaresize = 0.9,
       smlab = paste("Treatments versus Permethrin \n",
                     "By timing of outcome"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment",
       labels = labels)
```

### Mixed-effects meta-regression
```{r, echo = FALSE}
reg.outcometime <- rma(yi = y, sei = stderr, mods = as.factor(sg_outcometime), data = ires12_pairs, 
                       method = "REML", test = "knha")
reg.outcometime
```

### Sample sizes per subgroup
```{r, echo = FALSE}
with(ires12_long, sum(n[sg_outcometime == 1]))
with(ires12_long, sum(n[sg_outcometime == 2]))
```


# *Data management for sensitivity analyses*

## *Best case scenario*
```{r, echo = FALSE}
# Load dataset 
ires12_bcs <- read.csv("~/ires12_bcs.csv")

# Rename variables
names(ires12_bcs)[names(ires12_bcs) == "X_design"] <- "design"
names(ires12_bcs)[names(ires12_bcs) == "X_t1"] <- "t1"
names(ires12_bcs)[names(ires12_bcs) == "X_t2"] <- "t2"
names(ires12_bcs)[names(ires12_bcs) == "X_y"] <- "y"
names(ires12_bcs)[names(ires12_bcs) == "X_stderr"] <- "stderr"
names(ires12_bcs)[names(ires12_bcs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_bcs$ycorr <- (-1)*(ires12_bcs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_bcs <- merge(t1labels, ires12_bcs, by = "t1")
ires12_bcs <- merge(t2labels, ires12_bcs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_bcs <- merge(studychar, ires12_bcs, by = "study")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
sum(ires12_long$bcs_n)
```

## *Worst case scenario*
```{r, echo = FALSE}
# Load dataset 
ires12_wcs <- read.csv("~/ires12_wcs.csv")

# Rename variables
names(ires12_wcs)[names(ires12_wcs) == "X_design"] <- "design"
names(ires12_wcs)[names(ires12_wcs) == "X_t1"] <- "t1"
names(ires12_wcs)[names(ires12_wcs) == "X_t2"] <- "t2"
names(ires12_wcs)[names(ires12_wcs) == "X_y"] <- "y"
names(ires12_wcs)[names(ires12_wcs) == "X_stderr"] <- "stderr"
names(ires12_wcs)[names(ires12_wcs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_wcs$ycorr <- (-1)*(ires12_wcs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_wcs <- merge(t1labels, ires12_wcs, by = "t1")
ires12_wcs <- merge(t2labels, ires12_wcs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_wcs <- merge(studychar, ires12_wcs, by = "study")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
sum(ires12_long$wcs_n)
```

## *Excluding Adbel Raheem 2016*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Exclude inconsistent loops
ires12_pairs_cons4 <- filter(ires12_pairs, study!="ABD2016")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
ires12_long_cons4 <- filter(ires12_long, study!="ABD2016") 
sum(ires12_long_cons4$n)
```

## *Excluding Ahmad 2016*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Exclude inconsistent loops
ires12_pairs_cons1 <- filter(ires12_pairs, study!="AHM2016")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
ires12_long_cons1 <- filter(ires12_long, study!="AHM2016") 
sum(ires12_long_cons1$n)
```

## *Excluding Chhaiya 2012*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Exclude inconsistent loops
ires12_pairs_cons2 <- filter(ires12_pairs, study!="CHH2012")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
ires12_long_cons2 <- filter(ires12_long, study!="CHH2012") 
sum(ires12_long_cons2$n)
```

## *Excluding Ahmad 2016 and Chhaiya 2012*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Exclude inconsistent loops
ires12_pairs_cons3 <- filter(ires12_pairs, study!="AHM2016" & study!="CHH2012")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
ires12_long_cons3 <- filter(ires12_long, study!="AHM2016" & study!="CHH2012") 
sum(ires12_long_cons3$n)
```

## *Studies with preferred itch definition*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Subset to studies with preferred itch definition
ires12_pairs_itchdef <- filter(ires12_pairs, sensi_itchdef==0)

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")

ires12_long_itchdef0 <- filter(ires12_long, sensi_itchdef==0) 
sum(ires12_long_itchdef0$n)
```

## *Studies with low / some concerns risk of bias *
```{r, echo = FALSE}
# Load dataset 
ires12_pairs <- read.csv("~/ires12_pairs.csv")     # Contrast format

# Rename variables
names(ires12_pairs)[names(ires12_pairs) == "X_design"] <- "design"
names(ires12_pairs)[names(ires12_pairs) == "X_t1"] <- "t1"
names(ires12_pairs)[names(ires12_pairs) == "X_t2"] <- "t2"
names(ires12_pairs)[names(ires12_pairs) == "X_y"] <- "y"
names(ires12_pairs)[names(ires12_pairs) == "X_stderr"] <- "stderr"
names(ires12_pairs)[names(ires12_pairs) == "X_contrast"] <- "contrast"

# Correct direction of treatment effects
ires12_pairs$ycorr <- (-1)*(ires12_pairs$y)

# Combine with treatment labels
t1labels <- read.csv("~/t1labels.csv")
t2labels <- read.csv("~/t2labels.csv")
ires12_pairs <- merge(t1labels, ires12_pairs, by = "t1")
ires12_pairs <- merge(t2labels, ires12_pairs, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_v3.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs <- merge(studychar, ires12_pairs, by = "study")

# Subset to low/some concerns ROB
ires12_pairs_rob <- filter(ires12_pairs, sg_robbin==0)

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_v3.csv")
ires12_long_rob0 <- filter(ires12_long, sg_robbin==0)   # Subset long dataset to low/SC ROB
sum(ires12_long_rob0$n)
```

## *OIVM and PERM split dose*
```{r, echo = FALSE}
# Load dataset 
ires12_pairs_splitdose <- read.csv("~/ires12_splitdose.csv")   

# Rename variables
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_design"] <- "design"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_t1"] <- "t1"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_t2"] <- "t2"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_y"] <- "y"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_stderr"] <- "stderr"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_contrast"] <- "contrast"
names(ires12_pairs_splitdose)[names(ires12_pairs_splitdose) == "X_component"] <- "component"

# Correct direction of treatment effects
ires12_pairs_splitdose$ycorr <- (-1)*(ires12_pairs_splitdose$y)

# Combine with treatment labels
t1labels_splitdose <- read.csv("~/t1labels_splitdose.csv")
t2labels_splitdose <- read.csv("~/t2labels_splitdose.csv")
ires12_pairs_splitdose <- merge(t1labels_splitdose, ires12_pairs_splitdose, by = "t1")
ires12_pairs_splitdose <- merge(t2labels_splitdose, ires12_pairs_splitdose, by = "t2")

# Combine with study characteristics data
studychar <- read.csv("~/ires12_long_splitdose.csv")
studychar <- studychar[!duplicated(studychar$study), ]
ires12_pairs_splitdose <- merge(studychar, ires12_pairs_splitdose, by = "study")

# Obtain overall sample size
ires12_long <- read.csv("~/ires12_long_splitdose.csv")

sum(ires12_long$n)
```

