---
title: "Pairwise Meta-Analysis of Interventions for Scabies (Outcome: Itch resolution, 1-2 weeks)"
author: "Dr Amiel Nazer C. Bermudez"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
subtitle: "Oral IVM versus Permethrin"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
```

```{r, echo = FALSE}
# Load dataset for pairwise meta-analysis
ires_ma <- read.csv("~/ires12_ma_op.csv")
```

# **Meta-analysis proper**

## *Meta-analysis, random-effects model*
```{r, echo = FALSE, fig.width = 9}
# Fit model and summarise
ires12.meta <- 
  metabin(d.o, n.o, d.p, n.p, studlab, data = ires_ma,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(ires12.meta)

# Forest plot
forest(ires12.meta,
       studylab = TRUE,
       smlab = paste("Itch resolution, 1-2 weeks \n",
                     "Main analysis, RE model"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```


# **Sub-group analysis**

## *By risk of bias*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_robbin), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_robbin) %>% 
  summarise(n = sum(n))
```

## *By parasitological confirmation of diagnosis*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_paradx), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_paradx) %>% 
  summarise(n = sum(n))
```

## *By scabies treatment prior to trial entry*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_prevtx), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_prevtx) %>% 
  summarise(n = sum(n))
```

## *By presence of co-interventions*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_cointerv), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_cointerv) %>% 
  summarise(n = sum(n))
```

## *By industry funding*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_funding), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_funding) %>% 
  summarise(n = sum(n))
```

## *By % skin involvement*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_severebase), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_severebase) %>% 
  summarise(n = sum(n))
```

## *By timing of outcome*
```{r, echo = FALSE}
update.meta(ires12.meta, subgroup = as.factor(sg_outcometime), tau.common = FALSE)
```

### Sample sizes per subgroup
```{r, echo = FALSE}
ires12_long_OP %>% 
  group_by(sg_outcometime) %>% 
  summarise(n = sum(n))
```


# **Sensitivity Analyses**

## *Fixed-effects analysis*
```{r, echo = FALSE, fig.width = 9}
# Fit model and summarize
ires12.meta.fe <- 
  metabin(d.o, n.o, d.p, n.p, studlab, data = ires_ma,
          method = "Inverse", comb.fixed = TRUE, comb.random = FALSE, sm = "RR")
summary(ires12.meta.fe)

# Forest plot
forest(ires12.meta.fe,
       studylab = TRUE,
       smlab = paste("Itch resolution, 1-2 weeks \n",
                     "Fixed-effects model"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

## *Exclude other itch definition*
```{r, echo = FALSE, fig.width = 9}
# Subset to studies with preferred itch definition (sensi_itchdef==0)
ires_ma_itchdef <- filter(ires_ma, sensi_itchdef==0)

# Fit model and summarize
ires12.meta.itchdef <- 
  metabin(d.o, n.o, d.p, n.p, studlab, data = ires_ma_itchdef,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(ires12.meta.itchdef)

# Forest plot
forest(ires12.meta.itchdef,
       studylab = TRUE,
       smlab = paste("Itch resolution, 1-2 weeks \n",
                     "Preferred itch definition"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Sample sizes for sensitivity analysis
```{r, echo = FALSE}
with(ires12_long_OP, sum(n[sensi_itchdef == 0]))
```

## *Worst case scenario*
```{r, echo = FALSE, fig.width = 9}
# Fit model and summarize
ires12.meta.wcs <- 
  metabin(d.o.wcs, n.o.wcs, d.p.wcs, n.p.wcs, studlab, data = ires_ma,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(ires12.meta.wcs)

# Forest plot
forest(ires12.meta.wcs,
       studylab = TRUE,
       smlab = paste("Itch resolution, 1-2 weeks \n",
                     "Worst case scenario"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")

```

### Sample sizes for sensitivity analysis
```{r, echo = FALSE}
sum(ires12_long_OP$wcs_n)
```

## *Best case scenario*
```{r, echo = FALSE, fig.width = 9}
# Fit model and summarize
ires12.meta.bcs <- 
  metabin(d.o.bcs, n.o.bcs, d.p.bcs, n.p.bcs, studlab, data = ires_ma,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(ires12.meta.bcs)

# Forest plot
forest(ires12.meta.bcs,
       studylab = TRUE,
       smlab = paste("Itch resolution, 1-2 weeks \n",
                     "Best case scenario"),
       label.left = "Favours permethrin",
       label.right = "Favours treatment")
```

### Sample sizes for sensitivity analysis
```{r, echo = FALSE}
sum(ires12_long_OP$bcs_n)
```



