---
title: "Pairwise Meta-Analysis of Interventions for Scabies (Outcome: Clinical Cure, 1-2 Weeks)"
author: "Dr Amiel Nazer C. Bermudez"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
subtitle: "Oral IVM versus Permethrin"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
```

```{r, echo = FALSE}
# Load dataset 
cure12_pair_ma <- read.csv("~/cure12_pair_OP_rev.csv")
```

# **Meta-analysis proper**

## *Meta-analysis, random-effects model*
```{r, echo = FALSE, fig.width = 9, fig.height = 9}
# Fit model and summarise
cure12.meta <- 
  metabin(d.o, n.o, d.p, n.p, study, data = cure12_pair_ma,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(cure12.meta)

# Forest plot
forest(cure12.meta,
       studylab = TRUE,
       smlab = paste("Clinical cure, 1-2 weeks \n",
                     "Main analysis, RE model"),
       label.left = "Favours permethrin",
       label.right = "Favours oral IVM")
```


# **Sub-group analysis**

## *By parasitological confirmation of diagnosis*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(sg_paradx), tau.common = FALSE)
```

## *By scabies treatment prior to trial entry*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(sg_prevtx), tau.common = FALSE)
```

## *By dosing comparisons*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(dosecomp), tau.common = FALSE)
```

## *By presence of co-interventions*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(sg_cointerv), tau.common = FALSE)
```

## *By industry funding*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(sg_funding), tau.common = FALSE)
```

## *By timing of outcome*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(sg_outcometime), tau.common = FALSE)
```

## *By % skin involvement*
```{r, echo = FALSE}
update.meta(cure12.meta, subgroup = as.factor(ph_severebase), tau.common = FALSE)
```


# **Sensitivity Analyses**

## *Fixed-effects analysis*
```{r, echo = FALSE, fig.width = 9}
# Fit model and summarise
cure12.meta <- 
  metabin(d.o, n.o, d.p, n.p, study, data = cure12_pair_ma,
          method = "Inverse", comb.fixed = FALSE, comb.random = FALSE, sm = "RR")
summary(cure12.meta)

# Forest plot
forest(cure12.meta,
       studylab = TRUE,
       smlab = paste("Clinical cure, 1-2 weeks \n",
                     "Main analysis, FE model"),
       label.left = "Favours permethrin",
       label.right = "Favours oral IVM")
```

## *Excluding studies with high risk of bias*
```{r, echo = FALSE, fig.width = 9}
# Filter studies with low/some concerns ROB
cure12_pair_ma_lowscrob <- filter(cure12_pair_ma, sg_robbin==0)

# Fit model and summarise
cure12.meta.lowscrob <- 
  metabin(d.o, n.o, d.p, n.p, study, data = cure12_pair_ma_lowscrob,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(cure12.meta.lowscrob)

# Forest plot
forest(cure12.meta.lowscrob,
       studylab = TRUE,
       smlab = paste("Clinical cure, 1-2 weeks \n",
                     "Excludes high ROB studies"),
       label.left = "Favours permethrin",
       label.right = "Favours oral IVM")
```

## *Excluding studies with non-preferred outcome definitions*
```{r, echo = FALSE, fig.width = 9}
# Filter studies with low/some concerns ROB
cure12_pair_ma_curedef <- filter(cure12_pair_ma, cure_def==1)

# Fit model and summarise
cure12.meta.curedef <- 
  metabin(d.o, n.o, d.p, n.p, study, data = cure12_pair_ma_curedef,
          method = "Inverse", comb.fixed = FALSE, comb.random = TRUE, sm = "RR")
summary(cure12.meta.curedef)

# Forest plot
forest(cure12.meta.curedef,
       studylab = TRUE,
       smlab = paste("Clinical cure, 1-2 weeks \n",
                     "Preferred cure definition"),
       label.left = "Favours permethrin",
       label.right = "Favours oral IVM")
```