---
title: "Proportional Meta-Analysis of Baseline Cure Probabilities (1-2 Weeks) with Permethrin, All Doses"
author: "Amiel Nazer C. Bermudez, MD, MPH"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
library(rgl)
```

```{r, echo=FALSE}
# Load dataset 
cure_long <- read.csv("~/cure12_long_opsplit.csv")

# Subset to studies
cure_long_perm <- filter(cure_long, trt=="P")
cure_long_perm1 <- filter(cure_long, op_split=="P1")
cure_long_perm2 <- filter(cure_long, op_split=="P2")
cure_long_perm3 <- filter(cure_long, op_split=="P3")
```

# **Main analysis**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
cure.risk.perm <- metaprop(d, n, studlab = study, data = cure_long_perm,
                           sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                           method.incr = "only0", method.bias = "Egger",
                           fixed = FALSE, random = TRUE, 
                           outclab = "Cure, 1-2 weeks", complab = "Permethrin",
                           title = "Probability of cure")
cure.risk.perm

# Forest plot
forest(cure.risk.perm, layout = "RevMan5", xlab = "% cured",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

# **Sensitivity analyses**

## *Excluding studies with high risk of bias*
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
cure_long_perm_lowscrob <- filter(cure_long_perm, rob_bin==0)

# Fit PMA model
cure.risk.perm.lowscrob <- metaprop(d, n, studlab = study, data = cure_long_perm_lowscrob,
                                    sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                    method.incr = "only0", method.bias = "Egger",
                                    fixed = FALSE, random = TRUE, 
                                    outclab = "Cure, 1-2 weeks", complab = "Permethrin",
                                    title = "Excluding studies with high ROB")
cure.risk.perm.lowscrob

# Forest plot
forest(cure.risk.perm.lowscrob, layout = "RevMan5", xlab = "% cured",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

## *Excluding studies with non-preferred outcome definition*
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
cure_long_perm_curedef <- filter(cure_long_perm, cure_def==1)

# Fit PMA model
cure.risk.perm.curedef <- metaprop(d, n, studlab = study, data = cure_long_perm_curedef,
                                   sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                   method.incr = "only0", method.bias = "Egger",
                                   fixed = FALSE, random = TRUE, 
                                   outclab = "Cure, 1-2 weeks", complab = "Permethrin",
                                   title = "Excluding studies with non-preferred outcome definitions")
cure.risk.perm.curedef

# Forest plot
forest(cure.risk.perm.curedef, layout = "RevMan5", xlab = "% cured",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

## *Fixed-effects model*
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
cure.risk.perm.fe <- metaprop(d, n, studlab = study, data = cure_long_perm,
                              sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                              method.incr = "only0", method.bias = "Egger",
                              fixed = TRUE, random = FALSE, 
                              outclab = "Cure, 1-2 weeks", complab = "Permethrin",
                              title = "Fixed-effects model ")
cure.risk.perm.fe

# Forest plot
forest(cure.risk.perm.fe, layout = "RevMan5", xlab = "% cured",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```


# *Subgroup analyses*

## *Subgroup analysis by confirmation of parasitological diagnosis*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.paradx <- update(cure.risk.perm, subgroup = as.factor(sg_paradx))
sg.paradx
forest.meta(sg.paradx, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by prior treatment for scabies*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.prevtx <- update(cure.risk.perm, subgroup = as.factor(sg_prevtx))
sg.prevtx
forest.meta(sg.prevtx, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by dosing comparison*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.dosecomp <- update(cure.risk.perm, subgroup = as.factor(dosecomp))
sg.dosecomp
forest.meta(sg.dosecomp, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by simultaneous treatment of contacts*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.simultx <- update(cure.risk.perm, subgroup = as.factor(sg_simultx))
sg.simultx
forest.meta(sg.simultx, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by presence of cointerventions*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.cointerv <- update(cure.risk.perm, subgroup = as.factor(sg_cointerv))
sg.cointerv
forest.meta(sg.cointerv, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by presence of funding source*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.funding <- update(cure.risk.perm, subgroup = as.factor(sg_funding))
sg.funding
forest.meta(sg.funding, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by outcome timing*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.outcometime <- update(cure.risk.perm, subgroup = as.factor(sg_outcometime))
sg.outcometime
forest.meta(sg.outcometime, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by severity of baseline infestation*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.severebase <- update(cure.risk.perm, subgroup = as.factor(ph_severebase))
sg.severebase
forest.meta(sg.severebase, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```

## *Subgroup analysis by splitdose*
```{r, echo = FALSE, echo = FALSE, fig.height = 10, fig.width = 8}
sg.severebase <- update(cure.risk.perm, subgroup = as.factor(op_split))
sg.severebase
forest.meta(sg.severebase, addrows.below.overall = 2, subgroup.hetstat = TRUE)
```




