---
title: "Proportional Meta-Analysis of Baseline Probabilities of Itch Resolution (1-2 Weeks) with Permethrin"
author: "Amiel Nazer C. Bermudez, MD, MPH"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo = FALSE, include = FALSE}
library(metafor)
library(meta)
library(netmeta)
library(dplyr)
library(dmetar)
library(ggplot2)
library(gridExtra)
library(rgl)
```

```{r, echo=FALSE}
# Load dataset 
ires12_long <- read.csv("~/ires12_v2.csv")

# Subset to studies
ires12_long_perm <- filter(ires12_long, trt=="P")
ires12_long_perm1 <- filter(ires12_long, sensi_splitdose=="P1")
ires12_long_perm2 <- filter(ires12_long, sensi_splitdose=="P2")
ires12_long_perm3 <- filter(ires12_long, sensi_splitdose=="P3")
```

# ***PERMETHRIN, ALL DOSES***

# **Main analysis**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
ires12.risk.perm <- metaprop(d, n, studlab = study, data = ires12_long_perm,
                             sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                             method.incr = "only0", method.bias = "Egger",
                             fixed = FALSE, random = TRUE, 
                             outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin",
                             title = "Probability of itch resolution, 1-2 weeks")
ires12.risk.perm

# Forest plot
forest(ires12.risk.perm, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

# **Sensitivity analyses excluding studies with high risk of bias**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
ires12_long_perm_lowscrob <- filter(ires12_long_perm, sg_robbin==0)

# Fit PMA model
ires12.risk.perm.lowscrob <- metaprop(d, n, studlab = study, data = ires12_long_perm_lowscrob,
                                      sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                      method.incr = "only0", method.bias = "Egger",
                                      fixed = FALSE, random = TRUE, 
                                      outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin",
                                      title = "Excluding studies with high ROB")
ires12.risk.perm.lowscrob

# Forest plot
forest(ires12.risk.perm.lowscrob, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```


# ***PERMETHRIN, SINGLE-DOSE***

# **Main analysis**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
ires12.risk.perm1 <- metaprop(d, n, studlab = study, data = ires12_long_perm1,
                              sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                              method.incr = "only0", method.bias = "Egger",
                              fixed = FALSE, random = TRUE, 
                              outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, single-dose",
                              title = "Probability of itch resolution, 1-2 weeks")
ires12.risk.perm1

# Forest plot
forest(ires12.risk.perm1, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

# **Sensitivity analyses excluding studies with high risk of bias**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
ires12_long_perm1_lowscrob <- filter(ires12_long_perm1, sg_robbin==0)

# Fit PMA model
ires12.risk.perm1.lowscrob <- metaprop(d, n, studlab = study, data = ires12_long_perm1_lowscrob,
                                       sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                       method.incr = "only0", method.bias = "Egger",
                                       fixed = FALSE, random = TRUE, 
                                       outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, single-dose",
                                       title = "Excluding studies with high ROB")
ires12.risk.perm1.lowscrob

# Forest plot
forest(ires12.risk.perm1.lowscrob, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```


# ***PERMETHRIN, TWO-DOSE***

# **Main analysis**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
ires12.risk.perm2 <- metaprop(d, n, studlab = study, data = ires12_long_perm2,
                              sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                              method.incr = "only0", method.bias = "Egger",
                              fixed = FALSE, random = TRUE, 
                              outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, two-dose",
                              title = "Probability of itch resolution, 1-2 weeks")
ires12.risk.perm2

# Forest plot
forest(ires12.risk.perm2, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

# **Sensitivity analyses excluding studies with high risk of bias**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
ires12_long_perm2_lowscrob <- filter(ires12_long_perm2, sg_robbin==0)

# Fit PMA model
ires12.risk.perm2.lowscrob <- metaprop(d, n, studlab = study, data = ires12_long_perm2_lowscrob,
                                       sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                       method.incr = "only0", method.bias = "Egger",
                                       fixed = FALSE, random = TRUE, 
                                       outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, two-dose",
                                       title = "Excluding studies with high ROB")
ires12.risk.perm2.lowscrob

# Forest plot
forest(ires12.risk.perm2.lowscrob, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```


# ***PERMETHRIN, FLEXIDOSE***

# **Main analysis**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Fit PMA model
ires12.risk.perm3 <- metaprop(d, n, studlab = study, data = ires12_long_perm3,
                              sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                              method.incr = "only0", method.bias = "Egger",
                              fixed = FALSE, random = TRUE, 
                              outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, flexidose",
                              title = "Probability of itch resolution, 1-2 weeks")
ires12.risk.perm3

# Forest plot
forest(ires12.risk.perm3, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

# **Sensitivity analyses excluding studies with high risk of bias**
```{r, echo = FALSE, fig.height = 8, fig.width = 8}
# Filter to studies with low/some concerns risk of bias
ires12_long_perm3_lowscrob <- filter(ires12_long_perm3, sg_robbin==0)

# Fit PMA model
ires12.risk.perm3.lowscrob <- metaprop(d, n, studlab = study, data = ires12_long_perm3_lowscrob,
                                       sm = "PLOGIT", method = "Inverse", method.tau = "DL", 
                                       method.incr = "only0", method.bias = "Egger",
                                       fixed = FALSE, random = TRUE, 
                                       outclab = "Itch resolution, 1-2 weeks", complab = "Permethrin, flexidose",
                                       title = "Excluding studies with high ROB")
ires12.risk.perm3.lowscrob

# Forest plot
forest(ires12.risk.perm3.lowscrob, layout = "RevMan5", xlab = "% itch resolution",
       comb.random = TRUE, comb.fixed = FALSE, xlim = c(0,1), digits = 2, fontsize = 10,
       test.overall.common = FALSE, test.overall.random = TRUE,
       addrows.below.overall = 2)
```

